Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-06-27 main_revision.tex

\subsubsection{Water and N limitation across sites}
The four sites varied in the degree to which they are limited by water and N availability in the control state, with important impacts upon the parametric response characteristics (Figure \ref{btran state}). Water limitation in CLM5 can be expressed via the $B_{tran,mn}$ parameter, which is a model property calculated as a function of the prognostic leaf water potential. $B_{tran}$  is used to reduce assimilation and thus stomatal conductance by scaling the photosynthetic capacity, $V_{c,max}$. Given that leaf water potential and  $B_{tran}$ vary diurnally, we use the average daily minimum value here as a metric of drought stress (1 is no drought stress, 0 is total stomatal closure). For N limitation, the fraction of total NPP (where NPP is GPP-$r_{auto}$) that is used to pay for nitrogen uptake is a direct indicator of how N stress affects the carbon budget.

The Caxiuan\~a site experienced substantial drought stress in these simulations (with the mean $B_{tran,mn}$ of the default condition around $\sim$0.55), with little nutrient stress. The simulate forest at Niwot Ridge experienced substantial amounts of drought ($B_{tran,mn}$ $\sim$0.5), and N limitation, spending 27\% of net assimilated carbon on nutrient acquisition. Harvard Forest site had a moderate drought stress ($B_{tran,mn}$ $\sim$90\%), and moderate N limitation ($\sim$15\% of assimilation spent on uptake). The Metolius site had some drought stress ($B_{tran,mn}$ $\sim$86\%) and very little nutrient stress.  Differences in the initial conditions at the sites have implications for the parametric responses. Underlying limitations by various boundary conditions (water, nutrients, light, temperature) can affect both the ability of the system to respond to fertilization and/or parameter modifications affecting other resources, as we describe further in the following sections.

\subsubsection{Parametric control over system state}
At all sites, specific leaf area (\emph{slatop}) has a large first-order impact on LAI, and on leaf N concentrations (Figure \ref{NR1 state}), as expected since it is used directly in the calculation of both of these quantities. For GPP, the impact of SLA is always positive, despite the higher LAI causing lower N per unit area of leaf (which reduces per-unit leaf area photosynthetic capacity). The impact of SLA on NPP can, however, be negative (e.g., Metolius), since the fixed-fraction allometry model in CLM5 can generate shaded leaves that are in negative carbon balance at high LAI. At Niwot Ridge, the parameter range straddles an optimal SLA (or local maximum at the second-largest parameter values) for NPP, again reflecting the assimilation/respiration cost trade-off.

@@

Responses to modifications in \emph{grperc}, (the growth respiration coefficient) were in line with first-order expectations, where higher values resulted in NPP reductions and corresponding changes in LAI, and GPP. The impact varied between sites, reflecting different partitioning of the carbon budget into maintenance respiration, nitrogen uptake and growth.

@@

 \emph{cn\_flex\_c} affects the degree to which plants attempt to maintain tissue C:N values near to their target when environmental costs are varying. For the state impacts here, the role of this parameter was limited, but for the step-change fertilizations it was much more important, so we will discuss it's role further in the section below.

\subsection{CO$_{2}$ and Nitrogen deposition responses}
Figures \ref{GPP CO2 and N respones 2001}, \ref{NPP CO2 and N respones 2001} and \ref{LAI CO2 and N respones 2001} illustrate the responses to both N and to CO$_{2}$ fertilization simultaneously, for GPP, NPP and, LAI. Corresponding figures for vegetation carbon and $N_{area}$ are in the supplemental information (SI Figures 1 and 2). Figures for each site showing the individual N and CO$_{2}$ responses are also included in the SI (Figures 3 to 10).

>>>>

\subsubsection{Water and N limitation across sites}
The four sites varied in the degree to which they are limited by water and N availability in the control state, with important impacts upon the parametric response characteristics (Figure \ref{btran state}). Water limitation in CLM5 can be expressed via the $B_{tran,mn}$ parameter, which is a model property calculated as a function of the prognostic leaf water potential. $B_{tran}$  is used to reduce assimilation and thus stomatal conductance by scaling the photosynthetic capacity, $V_{c,max}$. Leaf water potential and  $B_{tran}$ vary diurnally, so we use the average daily minimum value here as a metric of drought stress (1 is no drought stress, 0 is total stomatal closure). For N limitation, the fraction of total NPP (where NPP is GPP-$r_{auto}$) that is used to pay for nitrogen uptake is a direct indicator of how N stress affects the carbon budget.

The Caxiuan\~a site experienced substantial drought stress in these simulations (with the mean $B_{tran,mn}$ of the default condition around $\sim$0.55), with little nutrient stress. The simulated forest at Niwot Ridge experienced substantial amounts of drought ($B_{tran,mn}$ $\sim$0.5), and N limitation, spending 27\% of net assimilated carbon on nutrient acquisition. Harvard Forest site had a moderate drought stress ($B_{tran,mn}$ $\sim$90\%), and moderate N limitation ($\sim$15\% of assimilation spent on uptake). The Metolius site had some drought stress ($B_{tran,mn}$ $\sim$86\%) and very little nutrient stress.  Differences in the initial conditions at the sites have implications for the parametric responses. Underlying limitations by various boundary conditions (water, nutrients, light, temperature) can affect both the ability of the system to respond to fertilization and/or parameter modifications affecting other resources, as we describe further in the following sections.

\subsubsection{Parametric control over system state}
At all sites, specific leaf area (\emph{slatop}) has a large first-order impact on LAI, and on leaf N concentrations (Figure \ref{NR1 state}), as expected, since it is used directly in the calculation of both of these quantities. For GPP, the impact of SLA is always positive, despite the higher LAI causing lower N per unit area of leaf (which reduces per-unit leaf area photosynthetic capacity). The impact of SLA on NPP can, however, be negative (e.g., Metolius), since the fixed-fraction allometry model in CLM5 can generate shaded leaves that are in negative carbon balance at high LAI. At Niwot Ridge, the parameter range straddles an optimal SLA (or local maximum at the second-largest parameter values) for NPP, again reflecting the assimilation/respiration cost trade-off.

@@

@@

 \emph{cn\_flex\_c} affects the degree to which plants attempt to maintain tissue C:N values near to their target when environmental costs are varying. For the state impacts here, the role of this parameter was limited, but for the step-change fertilization it was much more important, so we will discuss it's role further in the section below.

\subsection{CO$_{2}$ and Nitrogen deposition responses}

\subsubsection{Timescale dependance of responses to fertilization}

The initial changes in carbon economy induced by the fertilization experiments are, where conditions permit, amplified by increases in the leaf area index.  Figure \ref{timescales} illustrates, for the default parameter set, the evolution through time of output variables (GPP, NPP, LAI, $B_{tran,mn}$, NPP spent on N uptake). These results illustrate the complexities of the response.

For example, the initial stimulation of GPP by high CO$_{2}$ ($\sim$1.37) lead to a $\sim$50\% increase in LAI. This, however, lead to increase drought stress (lower $B_{tran,mn}$), and hence no large increase in GPP. At Metolious, in contrast, initial GPP stimulation was similar, the resulting growth in LAI was much slower, given the lower overall carbon turnover at this colder site. The 50\% increase in  carbon at 80 years had, however, a much larger impact on GPP, giving a stimulation of ** at 80 years. 
 At Harvard forest, the initial stimulation in the first year was lower (25\%) potentially on account of the higher carboxylation capacity at this site (as illustrated by the lower response to decreasing leaf C:N ratios in figure ** than other figures).  At all sites, the fraction of NPP spent on N uptake increased, but most dramatically at Metolius, where initial N expenditure was lowest initially on account of low growth rates.

As expected from the initial conditions, Niwot Ridge responded most strongly to nutrient additions. An initial NPP stimulation of 1.3 for NPP was magnified by subsequent increases in LAI to nearly 1.8 times the control value, causing a stimulation of 1.7 in NPP. None of the other sites exhibited such a dramatic change. In particular, Caxiuana, which was heavily water limited

Figures \ref{GPP CO2 and N respones 2001}, \ref{NPP CO2 and N respones 2001} and \ref{LAI CO2 and N respones 2001} illustrate the responses to both N and to CO$_{2}$ fertilization simultaneously, for GPP, NPP and, LAI. Corresponding figures for vegetation carbon and $N_{area}$ are in the supplemental information (SI Figures 1 and 2). Figures for each site showing the individual N and CO$_{2}$ responses are also included in the SI (Figures 3 to 10).
